### 2025-11-18 CV2/talks.tex

  \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://icomp.cc}{\em International Conference on Computational Optimization}, Abu Dhabi, United Arab Emirates (October 2025)

>>>>

  \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://icomp.cc}{\em International Conference on Computational Optimization 2025}, Abu Dhabi, United Arab Emirates (October 2025)
